---
title: "Diagnosing pre-analytical variation"
subtitle: "A detailed SomaScan workflow for processing-sensitive protein signatures, sample scoring, and filtering decisions"
author: "Subrata Paul"
bibliography: ../references.bib
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    number-sections: true
    smooth-scroll: true
    code-fold: true
    highlight-style: tango
    theme: cosmo
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
  cache: true
---

## Overview

SomaScan is a high-throughput aptamer-based proteomics platform capable of
measuring thousands of proteins simultaneously [@candia2025somascan]. Like other
blood-based proteomic assays, SomaScan measurements can be sensitive to
pre-analytical variation introduced during sample collection, processing,
handling, and storage [@tatsumi2026preanalytical; @candia2025hemolysis]. When
such variation is systematic — affecting a subset of samples differently — it
can produce spurious clusters in the data that are unrelated to the biological
question of interest.

This resource documents a set of diagnostic and remediation strategies for
identifying and handling pre-analytical variation in SomaScan data. The
methods are illustrated with examples from a multi-site asthma proteomics
study, but the approach generalises to any SomaScan dataset where sample
quality or processing history is a concern.

The SomaLogic-provided lists of processing-sensitive proteins (fed-fasted
state, freeze-thaw cycles, time to spin, time to decant, time to freeze) are
central to these methods. These lists are not redistributed here; they can be
obtained directly from SomaLogic. See the
[`data/README.md`](https://github.com/spaul-genetics/SomaSens/blob/main/data/README.md)
file for instructions on where to place them once obtained.

The examples in this resource use plasma SomaScan data from a multi-site
asthma proteomics study. The samples came from several collection sites, and
the unexplained split that motivated this workflow was most visible within the
Denver samples. I use Denver as the main worked example because that is where
the clustering problem was clearest. The methods themselves are not specific
to Denver; the same diagnostic and scoring steps can be applied to other
SomaScan datasets where sample handling or fasting status may have introduced
systematic structure.

---

## Diagnosing the Cause of Unexplained Sample Clusters {#sec-diagnosis}

### Motivation

After standard pre-processing and quality control, SomaScan data are often
subjected to dimensionality reduction (e.g., PCA) and unsupervised clustering
(e.g., k-means) to assess overall sample structure. In some datasets, two or
more clusters emerge that cannot be attributed to the primary experimental
variable (disease status, treatment arm, etc.) or to known technical factors
such as assay batch or collection site.

When this occurs, a natural question is: could a pre-analytical processing
difference — such as whether samples were collected from fasted or fed
subjects, or experienced different freeze-thaw histories — be responsible?

### Diagnostic Approach

SomaLogic provides, upon request, lists of proteins whose abundances are
known to change substantially under specific pre-analytical conditions. For
each condition, the list contains proteins along with their log2 fold change
relative to a reference condition (e.g., protein abundance after 12 hours of
fasting relative to the fed baseline).

The diagnostic approach works as follows:

1. **Quantify the between-group signal.** For each protein, fit a linear
   regression of log2 RFU on a categorical comparison variable, adjusting for
   relevant covariates (age, sex, disease status, ancestry PCs, assay batch).
   In the simplest case this is a binary contrast, but the grouping variable
   does not have to come from clustering. It can represent clusters, site,
   plate, processing group, or another experimental condition. The resulting
   beta coefficient for the selected contrast captures the direction and
   magnitude of each protein's difference between the two groups being compared.

2. **Compare to the processing-sensitive protein lists.** For each processing
   condition, plot the known processing-induced log2 fold change (x-axis)
   against the observed between-group beta coefficient (y-axis).

3. **Interpret the concordance.** If a processing condition explains the
   separation between the two groups, its sensitive proteins should fall
   predominantly in quadrants I (both positive) and III (both negative) of this
   plot — meaning proteins that go up under that processing condition are also
   more abundant in one group, and proteins that go down are less abundant in
   that same group. A pattern scattered across all four quadrants indicates
   that condition is not the driver.

### Example

The figure below shows this diagnostic applied to a subset of samples that
formed two clusters unexplained by experimental variables. Each panel
corresponds to one processing condition. The x-axis shows the known
processing-induced log2 fold change provided by SomaLogic; the y-axis shows
the observed cluster beta from the linear regression. Point size and colour
encode statistical significance (−log₁₀ adjusted p-value). To focus on the
most sensitive markers, each panel shows the five proteins with the largest
positive processing effect and the five proteins with the largest negative
processing effect, ranked by the x-axis fold-change column.

```{r}
#| label: fig-diag
#| fig-cap: >
#|   Diagnostic comparison of processing-sensitive protein fold changes
#|   (x-axis, from SomaLogic) versus observed between-cluster beta
#|   coefficients (y-axis). Each panel shows the five most positive and five
#|   most negative processing-sensitive proteins ranked by the SomaLogic
#|   x-axis fold-change column. Concordance in quadrants I and III implicates
#|   that condition as the likely driver of the sample clustering. In this
#|   example, only the Fed-Fasted State panel shows clear concordance,
#|   indicating that fasting status drove the observed clusters.
#| fig-width: 12
#| fig-height: 8

# ── Data requirement ──────────────────────────────────────────────────────────
# 01_cluster_diagnosis.r needs either:
#   (a) a pre-computed cache at data/de_cluster_results.rds  (fast path), OR
#   (b) an object called `adata_meta` already in the R environment.
#
# `adata_meta` must be a log2-transformed SomaScan ADAT joined with sample
# metadata, filtered to biological samples, and augmented with a 'Cluster'
# column ('Big' / 'Small') from a prior k-means step.
#
# To use the fast path, run 01_cluster_diagnosis.r once interactively with
# adata_meta loaded; it will write data/de_cluster_results.rds automatically.
# Subsequent renders (including this page) will read that cache instead.
# ─────────────────────────────────────────────────────────────────────────────

library(here)
source(here::here("scripts/01_cluster_diagnosis.r"))
print(diag_figure)
```

### Interpreting the Results

In the example above, only the **Fed-Fasted State** panel shows clear
concordance: proteins known to increase after fasting (positive
`Time_12_hours` fold change) were consistently more abundant in one cluster,
and proteins known to decrease after fasting were consistently less abundant
in that cluster. No such pattern was observed for freeze-thaw cycles, time to
spin, time to decant, or time to freeze.

This pattern strongly suggests that a subset of samples were collected from
subjects in a fasted state, while the remainder were collected from fed
subjects, and that this biological/pre-analytical difference — rather than
disease status or technical batch effects — is responsible for the clustering.

### Data Requirements

To run this diagnostic in your own dataset you need:

- **Log2-transformed SomaScan data** with a categorical comparison variable.
  A cluster label (`Big` / `Small`) is one example, but clustering is not a
  prerequisite. The same diagnostic can be used to compare site, plate,
  processing group, or another experimental condition. For the plotted
  diagnostic, the comparison should be a defined binary contrast or a selected
  coefficient from a multi-level categorical variable.
- **SomaLogic processing-sensitive protein lists** (CSV format, one file per
  condition). These are available from SomaLogic upon request and should be
  placed in the `data/` directory of this repository. They are excluded from
  version control; see
  [`data/README.md`](https://github.com/spaul-genetics/SomaSens/blob/main/data/README.md).
- **Sample metadata** including any covariates to be included in the linear
  model (e.g., age, sex, disease status, ancestry PCs, assay batch).

The annotated R script implementing this diagnostic is available at
[`scripts/01_cluster_diagnosis.r`](https://github.com/spaul-genetics/SomaSens/blob/main/scripts/01_cluster_diagnosis.r).

---

## Fed-Fasted Score Calculation {#sec-fed_fast_score}

### Motivation

The diagnostic plot above tells us which processing condition best matches
the unexplained sample clustering. In this example, the Fed-Fasted State panel
showed the clearest concordance: proteins known to increase after fasting were
also higher in one of the sample clusters, and proteins known to decrease
after fasting were lower in that same cluster.

After seeing that pattern, the next useful step is to turn the protein-level
signal into a sample-level score. The goal of the score is simple: for each
sample, estimate how strongly its protein profile looks like the fasted
pattern described by the SomaLogic fed-fasted experiment. This is consistent
with SOMAScan work showing that nutrient state can shift serum protein profiles
[@han2021nutrient].

### Score Definition

For both scoring strategies below, I use the same weighted score. Let
`R_sp` be the log2 RFU for sample `s` and protein `p`, let `mean(R_p)` be the
mean log2 RFU for protein `p` across samples, and let `beta_p` be the
SomaLogic fed-fasted effect size from `Time_12_hours`.

The score for sample `s` is:

$$
S_s = \sum_{p \in P} (R_{sp} - \bar{R}_p) \times \beta_p
$$

Here, `P` is the selected set of fed-fasted sensitive proteins. Centering each
protein first makes the score depend on whether a sample is high or low for
that protein relative to the dataset. Multiplying by `Time_12_hours` preserves
the direction of the fasting effect. A protein that increases after fasting
gets a positive weight, while a protein that decreases after fasting gets a
negative weight. In this way, both types of proteins contribute in the same
biological direction to the final score.

### Strategy 1: Effect-Size Thresholding

The first strategy is to keep fed-fasted proteins with stronger SomaLogic
effect sizes. Starting from the full fed-fasted CSV, we keep proteins with a
non-missing `Time_12_hours` value and then apply a threshold to the absolute
log2 fold change:

$$
|\beta_p| \geq c
$$

where `c` is the chosen effect-size cutoff. In this example, I scanned several
cutoffs based on the distribution of `abs(Time_12_hours)` and compared the
resulting score to the major PCA axis that captured the unexplained sample
split. The score remained strong when proteins with
`abs(Time_12_hours) >= 0.25` were used, while weaker-effect proteins were more
likely to add noise. For that reason, `0.25` is a practical default for this
example, not a universal rule.

This thresholding strategy is easy to understand and easy to reproduce. It
asks only one question: which proteins have a large enough known fed-fasted
effect that they should be trusted in the score?

### Strategy 2: Independent Protein Selection

The second strategy tries to avoid giving too much influence to groups of
highly correlated proteins. This is similar in spirit to clumping in PLINK.
In polygenic risk score analysis, clumping keeps the strongest genetic
variant in a correlated group and removes nearby variants that are in high
linkage disequilibrium. The aim is to keep the strongest signal without
counting the same correlated information many times [@chang2015plink].

Here the objects are proteins rather than genetic variants, so there is no
genomic window. Instead, I rank proteins by the absolute log2 fold change in
the SomaLogic `Time_12_hours` column. At each step, the protein with the
largest remaining `abs(Time_12_hours)` value is kept, and proteins that are
highly correlated with that selected protein are removed. The algorithm is:

1. Start with fed-fasted proteins with non-missing `Time_12_hours`.
2. From the proteins still available, select the one with the largest absolute
   `Time_12_hours` log2 fold change (`abs(Time_12_hours)`).
3. Remove any other available proteins that are too strongly correlated with
   the selected protein, using the chosen correlation threshold.
4. Repeat until no proteins remain.
5. Calculate the same weighted score using only the retained proteins.

I call the result an independent protein score. The word "independent" is
practical rather than absolute: the retained proteins are not guaranteed to be
statistically independent, but they are less redundant under the chosen
correlation threshold.

In this example, the correlation matrix used for clumping is estimated from
all sites except Denver. That choice matters. Denver is the site where the
fed-fasted-like split was most visible, so including Denver when estimating
protein-protein correlations can make proteins look correlated because of the
very artifact we are trying to measure. Using the non-Denver samples gives a
cleaner reference for deciding which proteins are redundant. In other settings,
the same correlation structure could also be estimated from publicly available
healthy-control SomaScan data, if the assay version and protein annotations are
compatible with the study being analyzed.

Several correlation thresholds can be tried, such as `0.60`, `0.75`, `0.80`,
and `0.90`. A lower threshold gives a smaller and less redundant protein set;
a higher threshold keeps more proteins and behaves more like the full
fed-fasted list. In the original analysis, correlation calculated without
Denver gave better separation of the suspected fed-fasted groups, especially
around the `0.75` threshold.

### Correlation Diagnostics

Before using the score, I like to look at the correlation structure of the
selected proteins. The first plot shows the proteins retained by the simple
`abs(Time_12_hours) >= 0.25` rule. The independent-protein tabs show the
clumping-like selection at several correlation thresholds. In all plots, the
upper triangle uses correlations calculated from all samples, while the lower
triangle uses correlations calculated after excluding Denver.

```{r}
#| label: setup-fedfast-scoring
#| include: false

source(here::here("scripts/02_fedfast_scoring.r"))
```

::: {.panel-tabset}

#### Log2 FC > 0.25

```{r}
#| label: fig-fedfast-cor-threshold-025
#| fig-cap: >
#|   Correlation among fed-fasted proteins selected by absolute SomaLogic
#|   Time_12_hours log2 fold-change threshold of 0.25. The upper triangle uses
#|   all samples and the lower triangle excludes Denver. Red labels indicate
#|   proteins higher after fasting; blue labels indicate proteins lower after
#|   fasting.
#| echo: false
#| fig-width: 9
#| fig-height: 8

plot_logfc_threshold_correlation(threshold = 0.25)
```

#### Independent: cor < 0.60

```{r}
#| label: fig-fedfast-cor-independent-060
#| fig-cap: >
#|   Color-coded correlation plot for independent fed-fasted protein selection
#|   using correlation threshold 0.60. The upper triangle uses all samples and
#|   the lower triangle excludes Denver. Red labels indicate proteins selected
#|   only when Denver is excluded, blue labels indicate proteins selected only
#|   when all samples are used, and purple labels indicate proteins selected in
#|   both cases.
#| echo: false
#| fig-width: 10
#| fig-height: 9

plot_independent_correlation(cor_threshold = 0.60)
```

#### Independent: cor < 0.75

```{r}
#| label: fig-fedfast-cor-independent-075
#| fig-cap: >
#|   Color-coded correlation plot for independent fed-fasted protein selection
#|   using correlation threshold 0.75. The upper triangle uses all samples and
#|   the lower triangle excludes Denver. Red labels indicate proteins selected
#|   only when Denver is excluded, blue labels indicate proteins selected only
#|   when all samples are used, and purple labels indicate proteins selected in
#|   both cases.
#| echo: false
#| fig-width: 10
#| fig-height: 9

plot_independent_correlation(cor_threshold = 0.75)
```

#### Independent: cor < 0.95

```{r}
#| label: fig-fedfast-cor-independent-095
#| fig-cap: >
#|   Color-coded correlation plot for independent fed-fasted protein selection
#|   using correlation threshold 0.95. The upper triangle uses all samples and
#|   the lower triangle excludes Denver. Red labels indicate proteins selected
#|   only when Denver is excluded, blue labels indicate proteins selected only
#|   when all samples are used, and purple labels indicate proteins selected in
#|   both cases.
#| echo: false
#| fig-width: 10
#| fig-height: 9

plot_independent_correlation(cor_threshold = 0.95)
```

:::

### Using The Score

Once the score is calculated, I use it as a QC summary of the fed-fasted
signal. A two-component Gaussian mixture model can be fit to the score to
identify samples with higher fasted-like signal versus lower fasted-like
signal [@benaglia2009mixtools]. Those labels can then be compared to PCA
clusters, collection site, and other metadata.

The plots below show the GMM fit for each score. The histogram shows the
score distribution, the black curves show the two fitted mixture components,
and the colored density curves show how the existing k-means clusters are
distributed along the score. The small table inside each plot summarizes how
many samples from each k-means cluster fall into the lower-score and
higher-score GMM groups.

::: {.panel-tabset}

#### Log2 FC > 0.25

```{r}
#| label: fig-fedfast-gmm-threshold-025
#| fig-cap: >
#|   Gaussian mixture model fit of the fed-fasted score calculated using
#|   proteins with absolute SomaLogic Time_12_hours log2 fold change greater
#|   than or equal to 0.25.
#| echo: false
#| fig-width: 8
#| fig-height: 5.8

plot_score_gmm(
  score_from_logfc_threshold(0.25),
  title = "GMM of score using |Time_12_hours| >= 0.25 proteins"
)
```

#### Independent: cor < 0.60

```{r}
#| label: fig-fedfast-gmm-independent-060
#| fig-cap: >
#|   Gaussian mixture model fit of the fed-fasted score calculated using
#|   independent proteins selected with correlation threshold 0.60. Protein
#|   correlations used for selection were calculated after excluding Denver.
#| echo: false
#| fig-width: 8
#| fig-height: 5.8

plot_score_gmm(
  score_from_independent_proteins(cor_threshold = 0.60),
  title = "GMM of independent-protein score, cor < 0.60"
)
```

#### Independent: cor < 0.75

```{r}
#| label: fig-fedfast-gmm-independent-075
#| fig-cap: >
#|   Gaussian mixture model fit of the fed-fasted score calculated using
#|   independent proteins selected with correlation threshold 0.75. Protein
#|   correlations used for selection were calculated after excluding Denver.
#| echo: false
#| fig-width: 8
#| fig-height: 5.8

plot_score_gmm(
  score_from_independent_proteins(cor_threshold = 0.75),
  title = "GMM of independent-protein score, cor < 0.75"
)
```

#### Independent: cor < 0.95

```{r}
#| label: fig-fedfast-gmm-independent-095
#| fig-cap: >
#|   Gaussian mixture model fit of the fed-fasted score calculated using
#|   independent proteins selected with correlation threshold 0.95. Protein
#|   correlations used for selection were calculated after excluding Denver.
#| echo: false
#| fig-width: 8
#| fig-height: 5.8

plot_score_gmm(
  score_from_independent_proteins(cor_threshold = 0.95),
  title = "GMM of independent-protein score, cor < 0.95"
)
```

:::

### Sample Filtering vs. Covariate Adjustment

After identifying samples with high fed-fasted score, there are two practical
ways to use this information in the downstream analysis.

The first option is sample filtering. In this approach, samples assigned to
the higher fed-fasted-score GMM group are removed before differential
expression analysis. This is useful when the score identifies a distinct
subset of samples that appears to be affected by a pre-analytical difference
rather than by the main biological question. The advantage is that we are not
asking the statistical model to repair a strong handling artifact after the
fact. The tradeoff is that we lose samples, and this can reduce power or
change the analysis population if the removed samples are not evenly
distributed across phenotypes, sites, or other study variables.

The second option is covariate adjustment. In this approach, all samples are
kept, and the fed-fasted score, or sometimes the GMM class based on the score,
is included as a covariate in the model. This can be attractive when the total
sample size is limited, when the score varies continuously rather than forming
a clear outlier group, or when filtering would remove too many samples from an
important subgroup. The tradeoff is that adjustment assumes the score captures
the processing effect in a way the model can handle. If the affected samples
form a strong separate cluster, or if the processing signal is highly
heterogeneous, a single covariate may not fully remove the artifact.

So I do not think there is one universal choice. The decision depends on the
experiment, the total number of samples, how much heterogeneity is present,
and how strongly the score is tangled with the biology we want to test. In
this example, the score and the PCA/k-means structure pointed to a smaller
group of samples with a clear fed-fasted-like signal. We found that filtering
was the better option for this dataset, so the smaller high-score group was
filtered out before the downstream differential expression analysis.

---

## Differential Expression After Fed-Fasted Filtering {#sec-de}

After filtering the smaller high-score group, the next question is how to run
the differential expression analysis. The data here are already normalized
SomaScan RFU values on the log2 scale, so we can use linear modeling methods
directly on the protein abundance matrix.

This is where `limma` is still a reasonable baseline model
[@ritchie2015limma]. We are not using `voom` here because `voom` was designed
mainly for RNA-seq-style count data, where the mean-variance relationship is
tied to count sampling and negative binomial-like behavior [@law2014voom].
SomaScan RFU values are not read counts. After the SomaScan normalization steps
and log2 transformation, the working data are continuous protein abundance
measurements, so the ordinary limma linear model with empirical Bayes variance
moderation is appropriate as a fixed-effect baseline.

However, this study includes samples from multiple sites. We saw earlier that
site contributed a large amount of structure to the proteomic data. A fixed
effect model can include site as a covariate, but that is not always the best
way to represent site-to-site heterogeneity, especially when the sites are
better thought of as sampled study centers with their own background shifts.
For that reason, we also tested random-effect models where site is included
as a random intercept.

The cleaned model helpers are in
[`scripts/03_de_analysis.r`](https://github.com/spaul-genetics/SomaSens/blob/main/scripts/03_de_analysis.r).
That script was organized from the older development scripts and contains:

- `fit_limma_model()` for the fixed-effect limma analysis without `voom`.
- `fit_dream_model()` for the mixed-effect Dream analysis with site as a
  random effect.
- `fit_lmer_test_model()` for a per-protein `lmerTest` comparison model.
- `fit_lmer_seq_model()` as an optional placeholder for an `lmerSeq`
  comparison model.
- `run_dream_all_samples()` and `run_dream_indep075_filter()` for the worked
  comparison used below.
- `volcano_break_axis()`, `plot_all_samples_dream_volcano()`, and
  `plot_indep075_dream_volcano()` for the volcano plots.

The important pattern from testing these approaches was that modeling site as
a random effect improved the signal compared with the fixed-effect limma
baseline. Among the random-effect approaches, Dream was the most useful for
this workflow because it combines linear mixed models with limma-style
empirical Bayes moderation [@hoffman2021dream].

We also used split eBayes in the Dream framework. SomaScan proteins are
measured in different dilution groups, and the technical variance structure is
not necessarily the same across those groups. Applying empirical Bayes
moderation separately within each dilution group lets the variance borrowing
happen within a more comparable set of measurements. In our analysis, this
split eBayes Dream model was more powerful than the alternatives we tested.

```{r}
#| label: setup-de-analysis
#| include: false

source(here::here("scripts/03_de_analysis.r"))
de_all_samples <- run_dream_all_samples()
de_indep075 <- run_dream_indep075_filter()

de_signal_count <- function(de_output, p_cutoff = 0.1, fc_cutoff = 0.25) {
  sum(
    de_output$results$adj.P.Val < p_cutoff &
      abs(de_output$results$logFC) >= fc_cutoff,
    na.rm = TRUE
  )
}

de_all_signal_count <- de_signal_count(de_all_samples)
de_filtered_signal_count <- de_signal_count(de_indep075)
```

The volcano plots below show the focused comparison used in this repo. The
first plot uses all samples. The second plot uses the same Dream split-eBayes
model after filtering samples by the independent fed-fasted score at
correlation threshold `0.75`. This keeps the model fixed and lets us see the
effect of removing the smaller high-score group.

The point of the all-sample plot is not that it produces many significant
proteins. It is the baseline comparison showing that, before filtering, the
asthma differential-expression signal is relatively muted. Using the same
display threshold shown in the volcano plots, `r de_all_signal_count` proteins
are highlighted in the all-sample model, compared with
`r de_filtered_signal_count` proteins after fed-fasted filtering. After
filtering, many more biologically meaningful proteins become visible, which is
why sample filtering was useful in this dataset.

IgE is an outlying signal in both dimensions: it has a very large log2 fold
change on the x-axis and a very large `-log10` adjusted p-value on the y-axis.
In a usual single-scale volcano plot, this stretches the axes so much that the
remaining proteins are compressed into a small part of the figure. For that
reason, we used a customized volcano plot with broken/faceted axes so that the
IgE result remains visible while the rest of the differential-expression
pattern can still be inspected.

::: {.panel-tabset}

#### After Fed-Fasted Filtering

```{r}
#| label: fig-de-dream-indep075-volcano
#| fig-cap: >
#|   Volcano plot for Active Asthma differential expression after filtering
#|   the higher-score GMM group identified from the independent fed-fasted
#|   score at correlation threshold 0.75. The model is Dream with site as a
#|   random effect and split empirical Bayes moderation by SomaScan dilution
#|   group. After filtering, more highlighted and biologically interpretable
#|   proteins become visible. Customized axis breaks are used because the IgE
#|   log2 fold change and adjusted significance are much larger than the rest
#|   of the proteins.
#| echo: false
#| fig-width: 10
#| fig-height: 7

plot_indep075_dream_volcano(de_indep075)
```

#### All Samples

```{r}
#| label: fig-de-dream-all-samples-volcano
#| fig-cap: >
#|   Volcano plot for Active Asthma differential expression using all samples.
#|   The model is Dream with site as a random effect and split empirical Bayes
#|   moderation by SomaScan dilution group. This panel is included as the
#|   baseline comparison before fed-fasted filtering; the broader asthma signal
#|   is relatively muted when all samples are retained. Customized axis breaks
#|   are used because the IgE log2 fold change and adjusted significance are
#|   much larger than the rest of the proteins.
#| echo: false
#| fig-width: 10
#| fig-height: 7

plot_all_samples_dream_volcano(de_all_samples)
```

:::

## References {.unnumbered}

::: {#refs}
:::

## Session Info {.unnumbered}

::: {.callout-note collapse="true"}
## Reproducibility Details

```{r}
#| label: session-info
#| echo: false
#| comment: ""

if (requireNamespace("sessioninfo", quietly = TRUE)) {
  sessioninfo::session_info()
} else {
  sessionInfo()
}
```

:::
